---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# biocroxytest

`r BiocStyle::Githubpkg("xec-cm/biocroxytest")` is an R package inspired by 
`r BiocStyle::Githubpkg("mikldk/roxytest")`. It is specifically designed for 
the development of Bioconductor packages that require tests with high execution 
times. 

This package extends the functionality of `roxytest` by introducing a new 
roclet, `@longtests`. This innovative feature allows developers to document and 
store these long tests directly in their `roxygen2` comments. 

With `r BiocStyle::Githubpkg("xec-cm/biocroxytest")`, developers can now write 
comprehensive tests without worrying about slowing down the daily build process. 
The `@longtests` roclet provides a dedicated space for these extensive tests, 
ensuring they are easily accessible and well-documented. This approach not only 
improves the reliability of the package but also enhances its maintainability. 
Developers can easily locate, understand, and update these long tests as needed,
leading to more robust and efficient code.

## Installation instructions

Get the latest stable `R` release from [CRAN](http://cran.r-project.org/). Then 
install `biocroxytest` from [Bioconductor](http://bioconductor.org/) using the 
following code:

```{r 'install', eval = FALSE}
# Not yet on Bioconductor
# if (!requireNamespace("BiocManager", quietly = TRUE)) {
#     install.packages("BiocManager")
# }
# 
# BiocManager::install("biocroxytest")
```

And the development version from [GitHub](https://github.com/xec-cm/biocroxytest) with:

```{r 'install_dev', eval = FALSE}
BiocManager::install("xec-cm/biocroxytest")
```

## Example

Here is how you can use `r BiocStyle::Githubpkg("xec-cm/biocroxytest")` to 
create a new package with long tests:

To use the package in your own package you do not need to add any additional 
dependencies in your package’s DESCRIPTION file. Simply add the following lines 
to your package’s DESCRIPTION file (along with Suggests: testthat):

```
Roxygen: list(roclets = c("namespace", "rd", "biocroxytest::longtests_roclet"))
```

Then add `@longtests` to the roxygen comments of the functions you want to test. 
For example, if the file `R/functions.R` contains this code:

```{r, eval=FALSE}
#' A function to do x
#' 
#' @param x A number
#' 
#' @longtests 
#' expect_equal(foo(2), sqrt(2))
#' expect_error(foo("a string"))
#' 
#' @return something
foo <- function(x) {
  return(sqrt(x))
}

#' A function to do y
#' 
#' @param x Character vector
#' @param y Character vector
#' 
#' @longtests 
#' expect_equal(bar("A", "B"), paste("A", "B", sep = "/"))
#' 
#' @export
bar <- function(x, y) {
  paste0(x, "/", y)
}
```

Then `roxygen2::roxygenise()` will generate (with the `longtests_roclet` roclet) 
the file `longtests/test-biocroxytest-tests-functions.R` with this content:

```{r, eval=FALSE}
# Generated by biocroxytest: do not edit by hand!

# File R/functions.R: @longtests

test_that("Function foo() @ L11", {
  expect_equal(foo(2), sqrt(2))
  expect_error(foo("a string"))
})


test_that("Function bar() @ L27", {
  expect_equal(bar("A", "B"), paste("A", "B", sep = "/"))
})
```

## Code of Conduct

Please note that the `r BiocStyle::Githubpkg("xec-cm/biocroxytest")` project is 
released with a [Contributor Code of Conduct](http://bioconductor.org/about/code-of-conduct/). 
By contributing to this project, you agree to abide by its terms.



