---
title: "Introduction to biocroxytest"
output: rmarkdown::html_vignette
description: |
  Start here if this is your first time using biocroxytest! You will learn about     basic usage.
vignette: >
  %\VignetteIndexEntry{Introduction to biocroxytest}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style>
body {
text-align: justify}
</style>

```{r, include = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  digits = 3,
  collapse = TRUE,
  comment = "#>"
)
options(digits = 3)
```

# Introduction

`r BiocStyle::Githubpkg("xec-cm/biocroxytest")` is an R package inspired by 
`r BiocStyle::Githubpkg("mikldk/roxytest")`. It is specifically designed for 
the development of Bioconductor packages that require tests with high execution 
times. 

This package extends the functionality of `roxytest` by introducing a new 
roclet, `@longtests`. This innovative feature allows developers to document and 
store these long tests directly in their `roxygen2` comments. 

With `biocroxytest`, developers can now write comprehensive tests without 
worrying about slowing down the daily build process. The `@longtests` roclet
provides a dedicated space for these extensive tests, ensuring they are easily 
accessible and well-documented. This approach not only improves the reliability 
of the package but also enhances its maintainability. Developers can easily 
locate, understand, and update these long tests as needed, leading to more 
robust and efficient code.

## Session info

```{r}
devtools::session_info()
```

