---
title: "Introduction to biocroxytest"
output: rmarkdown::html_vignette
description: |
  Start here if this is your first time using biocroxytest! You will learn about     
  basic usage.
vignette: >
  %\VignetteIndexEntry{Introduction to biocroxytest}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: 72
---

```{=html}
<style>
body {
text-align: justify}
</style>
```
```{r, include = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  digits = 3,
  collapse = TRUE,
  comment = "#>"
)
options(digits = 3)
```

# Introduction

`r BiocStyle::Githubpkg("xec-cm/biocroxytest")` is an R package inspired
by `r BiocStyle::Githubpkg("mikldk/roxytest")`. It is specifically
designed for the development of Bioconductor packages that require tests
with high execution times (longtests).

This package extends the functionality of `roxytest` by introducing a
new roclet, `@longtests`. This innovative feature allows developers to
document and store these long tests directly in their `roxygen2`
comments.

With `biocroxytest`, developers can now write comprehensive tests
without worrying about slowing down the daily build process. The
`@longtests` roclet provides a dedicated space for these extensive
tests, ensuring they are easily accessible and well-documented. This
approach not only improves the reliability of the package but also
enhances its maintainability. Developers can easily locate, understand,
and update these long tests as needed, leading to more robust and
efficient code.

## Session info

```{r}
utils::sessionInfo()
```
